Excel fun

### 2022-07-12 Excel fun.Rmd
pivot_wider - entries as columns.
Deleting unnecessary file read. Adding logical test.

## Long vs. wide data
![](Images/wideLong1-1.png)

Fra [Statology](https://www.statology.org/long-vs-wide-data/).

@@

## Wide file

```{r}
wide_data <- read_excel("Data/Book1.xlsx")
wide_data
wide_data |> 
  filter(!is.na(Year))
```

>>>>

@@

## `pivot_wider()`
```{r}
test4 <- test2 |>
  unite(entry, c(category, entry), sep = " ") |> 
  select(-year) |> 
  pivot_wider(names_from = entry, values_from = value)

test4

test4 |> 
  summarise(
    sum = sum(`Revenue Private contributions`:`Revenue Other`)
  ) |> 
  summarise(
    test = sum == test4$`Revenue Sum total revenue`)
```
